\section{Frequency of Java Dependencies}
\label{appendix:frequency-of-java-dependencies}

{\small This is an edited version of my original article as posted on my personal website: http://www.jeroenpeeters.nl/articles/frequency-of-java-dependencies/}.

\subsection{The Approach}

Github exposes an API through which you can search for projects with a certain language, rating, etc. Furthermore it is possible to query a project’s tree structure and obtain file data.

Because I needed a representative data set I choose to include mature and active projects only. For this purpose a project is considered active if it had at least one commit in the last year. Secondly a project is considered mature if it is older than at least one year.

The Java world has three major build and dependency management tools; Maven, Gradle and Ivy. I simply downloaded the according build files to obtain dependency related information.

For each Github project each dependency is only counted once. This means that if a project contains multiple modules each having its own dependency management, duplicated dependencies are counted as one occurrence. Furthermore, build tools specific dependencies (such as maven-compiler-plugin) are omitted from the results. This is because depending on these artifacts is a consequence of using the build tool. They would thus occur frequently and cloud the results.

\subsection{The Results}

From the years 2008 to 2012 I was able to retrieve 3.029 projects with dependency management files (of which 2502 (82\%) Maven projects, 430 (14\%) Gradle projects and 97 (3\%) Ant+Ivy projects).

From these figures it is not difficult to conclude that the majority of Java projects use Maven as a build and dependency management tool.

These projects had a total of 26.235 unique dependencies. The following list details the top 5 projects on which others depend:

\begin{itemize}
	\item junit - 1883
	\item slf4j-api - 764
	\item oss-parent - 700
	\item log4j - 671
	\item commons-io - 543
\end{itemize}

The following graphic shows the top 25 most depended on projects. We observe that JUnit is by far the most depended on artifact, followed by sfl4j-api and oss-parent.

We can see that a large portion of these top projects are related to testing (junit, mockito-all, spring-test, mockito-core) and logging (sfl4j-api, log4j, slf4j-log4j12, commong-logging, logback-classic).

\subsection{The code}

To obtain and analyze the Github data I had to implement two relatively small programs. Both of them are freely available under the GNU GPL from, off course, Github.

\begin{itemize}
	\item https://github.com/jeroenpeeters/github-dependency-analyzer
\end{itemize}

\subsection{The data}

The full data set contains 25.243 projects. Table \ref{table:dependency-frequency} lists the first 30 projects from the data set with their dependency frequency.
The complete data set, in raw and analyzed form, can be downloaded from the above mentioned Github repository. 

\begin{table}
	\centering
	\begin{tabular}{ | l | l | }
	    \hline
	    \textbf{Project name} & \textbf{Dependency count} \\ \hline
	    junit & 1883 \\ \hline
	    slf4j-api & 764 \\ \hline	
	    oss-parent & 700 \\ \hline
	    log4j & 671 \\ \hline
	    commons-io & 543 \\ \hline
	    guava & 520 \\ \hline
	    servlet-api & 489 \\ \hline
	    slf4j-log4j12 & 482 \\ \hline
	    commons-lang & 444 \\ \hline
	    commons-logging & 436 \\ \hline
	    mockito-all & 385 \\ \hline
	    commons-codec & 335 \\ \hline
	    lifecycle-mapping & 333 \\ \hline
	    spring-context & 332 \\ \hline
	    httpclient & 290 \\ \hline
	    spring-test & 288 \\ \hline
	    logback-classic & 284 \\ \hline
	    joda-time & 283 \\ \hline
	    jackson-mapper-asl & 273 \\ \hline
	    jcl-over-slf4j & 264 \\ \hline
	    testng & 263 \\ \hline
	    spring-core & 263 \\ \hline
	    mockito-core & 261 \\ \hline
	    android & 244 \\ \hline
	    spring-beans & 235 \\ \hline
	    spring-web & 234 \\ \hline
	    commons-collections & 228 \\ \hline
	    hsqldb & 218 \\ \hline
	    spring-webmvc & 216 \\ \hline
	    mysql-connector-java & 215 \\ \hline
	\end{tabular}
	\caption{Dependency frequency: Thirty most depended-on projects}
	\label{table:dependency-frequency}
\end{table}
